---
title: "Wk 09: Network Analysis"
---



## Overview: Network Analysis 

Web of Science Queries (articles only)

* [Technical Communication Quarterly](https://www.webofscience.com/wos/woscc/summary/6c31f851-fec2-4b2b-8003-01b6f836bbac-afc4d4e3/relevance/1)
* [IEEE Transactions on Professional Communication](https://www.webofscience.com/wos/woscc/summary/13106b03-1f1a-4c9e-a2c9-03080436c96e-afc513aa/relevance/1)
* [Journal of Business and Technical Communication](https://www.webofscience.com/wos/woscc/summary/840d8fbb-d74a-4b94-ba44-eded28ce8cbb-afc883f2/relevance/1)
* [Technical Communication](https://www.webofscience.com/wos/woscc/summary/1b978d9b-135d-4b10-b377-b7340f59d9ef-afc88e9b/relevance/1)

Other resources:

* [Article that presents a tutorial for Bibliometrix](https://dergipark.org.tr/en/download/article-file/2237066)

## Key library: Bibliometrix

[Bibliometrix](https://www.bibliometrix.org/home/)

```{r}
library(tidyverse)
library(janitor)
library(bibliometrix)

```

To use biblioshiny (Graphical interface built with RShiny)
```{r}
#library(bibliometrix)
#biblioshiny()
```


## Convert .bib to dataframes

Set file locations
```{r}
tcq <- "data/wos-tcq.bib"
ieee <- "data/wos-ieee.bib"
jbtc <- "data/wos-jbtc.bib"
tc <- "data/wos-tc.bib"
```

Convert each bib file to a dataframe

```{r}
#help(convert2df)


# TCQ
df_tcq <- convert2df(file = tcq,
                  dbsource = "wos",
                  format = "bibtex")

# IEEE
df_ieee <- convert2df(file = ieee,
                  dbsource = "wos",
                  format = "bibtex")

# JBTC
df_jbtc <- convert2df(file = jbtc,
                  dbsource = "wos",
                  format = "bibtex")

# TC
df_tc <- convert2df(file = tc,
                  dbsource = "wos",
                  format = "bibtex")
```

Combine the resulting dataframes

```{r}
M <- bind_rows(
  df_ieee,
  df_jbtc,
  df_tc,
  df_tcq
)

#write_rds(M, "data/comb.rds")

#install.packages("bib2df")
#library(bib2df)
#df2bib(M, "data/comb.bib")

#write_csv(M, "data/comb.csv")

# get subset for analysis

M <- M %>%
  filter(PY > 1992)
```


```{r}
# run a stock analysis (generates a list of dataframes)
results <- biblioAnalysis(M, sep = ";")

# create a summary of the results
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
```
# Plot results

```{r}
plot(x = results, k = 10, pause = FALSE)
```

## Citation analysis

Most cited articles

```{r}
# Get citations
CR <- citations(M, field = "article", sep = ";")

# Top 50 most cited articles
cbind(CR$Cited[1:50])
```

Most cited first authors

```{r}
CR <- citations(M, field = "author", sep = ";")

cbind(CR$Cited[1:25])
```

### Local citations

Not working :(
```{r}
CR <- localCitations(M, sep = ";")
CR$Authors[1:10, ]
```
Not working :(
```{r}
CR$Papers[1:10,]
```
```{r}
DF <- dominance(results, k = 12)
DF
```

```{r}
topAU <- authorProdOverTime(M, k = 20, graph = TRUE)
```
```{r}
head(topAU$dfAU)
```
## Co-Citation

```{r}

NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")

## Plot the network
net=networkPlot(NetMatrix,
                n = 25, 
                Title = "Co-Citation Network", 
                type = "fruchterman", 
                size=T,
                label.cex=TRUE,
                label.color=TRUE,
                halo=FALSE,
                remove.multiple=FALSE, 
                labelsize=.7,
                edgesize = 3,
                cluster = "none",
                community.repulsion = .3,
                edges.min = 1)

```






