---
title: "Wk 09: Network Analysis, pt 2"
---

```{r}
library(tidyverse)
library(bibliometrix)
library(stringr)
```


Read in combined data

```{r}
M <- read_rds("data/comb.rds")
```


## Create subsets for analysis

We can manipulate the data here and then explore further with bibliometrix.

Here is a list of [WOS/Bibliometrix tags](https://www.bibliometrix.org/documents/Field_Tags_bibliometrix.pdf), for reference. Some key tags:

* PY: publication year
* TI: document title
* AU: authors
* DE: author-supplied keywords
* AB: abstract
* CR: list of cited references
* NR: count of cited references

### Filter articles by publication year

```{r}
# Only articles after 1992

post92 <- M %>%
  filter(PY > 1992)

```


### Filter articles by "word" in title

```{r}
word <- "ethics"

ethics <- M %>%
  filter(str_detect(TI, regex(word, ignore_case = TRUE)))


```

### Filter articles by one or more words in abstract

```{r}
search_terms <- c("Aristotle", "Plato", "Socrates")  # List of words to check for

# create a regular expression pattern by pasting the search terms together and separating them with \\b|\\b. The \\b is a word boundary anchor, ensuring that we match whole words or phrases rather than substrings 
pattern <- paste0("\\b", paste(search_terms, collapse = "\\b|\\b"), "\\b")

greeks <- M %>%
  filter(str_detect(AB, regex(pattern, ignore_case = TRUE)))

greeks$AB
```

### Filter articles that contain one of the keywords in either title or abstract

```{r}
search_words <- c("Intersectionality", "Intersectional")

# Filter the data frame to select rows with at least one word from the list in column1 or column2
intersectional <- M %>% 
  rowwise() %>%
  filter(any(str_detect(c(TI, AB), regex(paste(search_words, collapse = "|"), ignore_case = TRUE))))

intersectional$TI
         
```

## Explore new data in bibliometrix

Take the result of your filtering and analyze it!

### Stock descriptive analysis

```{r}
# run a stock analysis (generates a list of dataframes)
results <- biblioAnalysis(intersectional, sep = ";")

# create a summary of the results
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
```
```{r}
#plot(x = results, k = 10, pause = FALSE)
```
### Citation analysis

When writing about intersectionality, who do TC authors cite?

#### Most cited articles

```{r}
# Get citations
CR <- citations(intersectional, field = "article", sep = ";")

# Top 50 most cited articles
cbind(CR$Cited[1:50])
```
#### Most cited first authors

```{r}
CR <- citations(intersectional, field = "author", sep = ";")

cbind(CR$Cited[1:20])
```



