---
title: "Wk 05: Titles in TC Journals, pt. 1"
---

## Overview

Here, we prepare a dataset consisting of article metadata for five major tc journals:

* Journals: Technical Communication Quarterly (TCQ), Technical Communication (TC), Journal of Technical Writing and Communication (JTWC)
, Communication Design Quarterly (CDQ), and Journal of Business and Technical Communication (JBTC)
* Years: 2005 - 2023
* Article Metadata: Journal, Authors, Title, Abstract, Publication Year

## Prepare data

We need to drop written comm from our "full data" and read in and clean bibtex data from Communication Design Quarterly and Journal of Technical Writing and Communication

### Load libraries

```{r}
#install.packages("bib2df")
library(bib2df)
library(janitor)
library(tidyverse)
```
First, we'll read in CDQ.
```{r}
# CDQ: read in and clean names
cdq_raw <- bib2df("data/acm-cdq.bib")%>%
  clean_names()

head(cdq_raw)
```


Second, we'll read in JWTC.
```{r}
# JWTC: read in and clean names
jtwc_raw <- bib2df("data/jtwc.bib")%>%
  clean_names()

head(jtwc_raw)
```


Third, we'll read in our full data and drop WC
```{r}
# read in full data and drop Written Comm entries
fullish <- read_csv("data/full_data.csv") %>%
  filter(abbreviation != "WC") %>%
  select(source_title,
         author_full_names,
         article_title,
         abstract,
         publication_year,
         abbreviation)

#head(fullish)

#glimpse(fullish)

#unique(fullish$abbreviation)
```

### Unify the dataset

For this analysis, we want consistent data and column names for each journal in the dataset. Here are the datapoints, using the column names from our preexisting data:

* source_title
* author_full_names
* article_title
* abstract
* publication_year
* abbreviation

Let's select the target fields, add the journal abbreviation, and rename the columns to harmonize the data with our preexisting set. 
```{r}
#glimpse(cdq_raw)

# select fields to keep; add an abbreviation column; rename columns
cdq_select <- cdq_raw %>%
  select(journal,
         author,
         title,
         abstract,
         year) %>%
  mutate(abbreviation = "CDQ")%>%
  rename(source_title = journal,
         author_full_names = author,
         article_title = title,
         abstract = abstract,
         publication_year = year,
         abbreviation = abbreviation)%>%
  mutate(author_full_names = map_chr(author_full_names, ~ paste(.x, collapse = "; ")))

glimpse(cdq_select)

```

Now the same for JTWC!
```{r}
#glimpse(jtwc_raw)

# select fields to keep; add an abbreviation column; rename columns
jtwc_select <- jtwc_raw %>%
  select(journal,
         author,
         title,
         abstract,
         year) %>%
  mutate(abbreviation = "JTWC")%>%
  rename(source_title = journal,
         author_full_names = author,
         article_title = title,
         abstract = abstract,
         publication_year = year,
         abbreviation = abbreviation)%>%
  mutate(author_full_names = map_chr(author_full_names, ~ paste(.x, collapse = "; ")))

glimpse(jtwc_select)

```

Now we can join the three

```{r}
tc_journals <- bind_rows(fullish, cdq_select, jtwc_select)

glimpse(tc_journals)
```
## Check work: Plot the data

```{r}
# Plot 1: Count of observations by journal abbreviation
tc_journals %>%
  count(abbreviation) %>%
  ggplot(aes(x = reorder(abbreviation, n), y = n)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +
  labs(title = "Articles published (2005-2023) in major TC Journals", x = "Journal", y = "Articles")
```
```{r}
# Plot 2: Bar chart of the number of articles published per year, colored by journal abbreviation
tc_journals %>%
  group_by(publication_year, abbreviation) %>%
  summarise(num_articles = n()) %>%
  ggplot(aes(x = publication_year, y = num_articles, fill = abbreviation)) +
  geom_bar(stat = "identity") +
  labs(title = "Articles Published per Year, by Journal Abbreviation", x = "Publication Year", y = "Number of Articles") +
  scale_fill_discrete(name = "Journal Abbreviation")
```
```{r}
# Plot 3: Dot plot of the number of articles published per year, colored by journal abbreviation with trend lines
tc_journals %>%
  group_by(publication_year, abbreviation) %>%
  summarise(num_articles = n()) %>%
  ggplot(aes(x = publication_year, y = num_articles, color = abbreviation)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, size = .7, aes(group = abbreviation), linetype = "dashed") +
  labs(title = "Articles Published per Year, by Journal Abbreviation", x = "Publication Year", y = "Number of Articles") +
  scale_color_discrete(name = "Journal Abbreviation")
```


```{r}
# Plot 4: Bar chart of articles per year
tc_journals %>%
  group_by(publication_year) %>%
  summarise(num_articles = n()) %>%
  ggplot(aes(x = publication_year, y = num_articles)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Total Articles per Year across Major TC Journals", x = "Publication Year", y = "Number of Articles")
```

## Write out new data

```{r}
# save as csv

write_csv(tc_journals, "data/tc_journals.csv")


save(tc_journals, file = "data/tc_journals.RData")
```

